\documentclass[11pt]{exam}

\usepackage{listings}
\usepackage{graphicx}
\usepackage{color}


\lstdefinestyle{latexsty}{
	language={[LaTeX]TeX},
    basicstyle=\small\ttfamily,
    breaklines=true,
    breakindent=0pt, 
    numbers=left, stepnumber=1, numbersep=5pt,
    commentstyle=\color{red},
    showstringspaces=false,
    keywordstyle=\color{blue}\bfseries,
    morekeywords={align,begin},
    tabsize=2,
    frame=single,
}

\pagestyle{headandfoot}
\runningheader{\LaTeX: An Introduction (Part 2)}{Exercise 3}{21st February 2014}
\runningheadrule
\runningfooter{}{\thepage}{}
\runningfootrule

\title{Exercise 2 - Floating Environments}
\author{UGC `\LaTeX: An Introduction (Part 2)' Training Course}
\date{February 21st 2014}


\begin{document}
\maketitle

\fbox{\parbox{0.9\textwidth}{In this exercise, we will look at including graphics in our \LaTeX\ documents..}}

\vspace{0.2in}

\begin{questions}
\question
If it's not already open, open TeXworks. Either create a new file for this exercise and save it somewhere appropriate, or open an existing file.
\question
Find a picture somewhere that you would like to include in your document. Google image search is a good place to start looking.
\question
Save the picture in the same folder as your \LaTeX\ document.
\question
Add the \texttt{graphicx} package to your document and use the \texttt{{\textbackslash}includegraphics} command to include the image you just saved in your document.
\question
Repeat the process and add another image to your document
\question
Place a \texttt{figure} environment around one of the images you added previously.
\question
Add a caption and a label to the figure.
\uplevel
{From here on it will be beneficial if your document includes some large portions of text. If you have started with a blank document, add some text to your document before continuing. (You can copy and paste the text from wherever you like).}
\question
Experiment with placing the \LaTeX\ source code for your figure at different points in the document. Where does \LaTeX\ move it to after compiling? 
\question
What effect does changing the position specifier have?
\question
Add a new figure containing two or more subfigures to your document. 
\question
Can you refer to your figures within the text of your document? Is the numbering correct?
\question
Experiment with the subfigure layout. Can you create a 4x4 grid of images? Can you arrange three images vertically?
\question
Change your document to be double-column. Can you make your figures stretch across both columns?
\question 
Create a table and wrap it in a \texttt{table} environment. Add a label and a caption to it. Can you then refer to that table in the text with a cross reference?
\question
Experiment with the position specifier on the \texttt{table} environment to see how \LaTeX\ positions your floating table.
\end{questions}

\end{document}