\documentclass[11pt]{exam}

\usepackage{listings}
\usepackage{graphicx}
\usepackage{color}
\usepackage{dtklogos}
\usepackage[T1]{fontenc}

\lstdefinestyle{latexsty}{
	language={[LaTeX]TeX},
    basicstyle=\small\ttfamily,
    breaklines=true,
    breakindent=0pt, 
    numbers=left, stepnumber=1, numbersep=5pt,
    commentstyle=\color{red},
    showstringspaces=false,
    keywordstyle=\color{blue}\bfseries,
    morekeywords={align,begin},
    tabsize=2,
    frame=single,
}

\pagestyle{headandfoot}
\runningheader{\LaTeX: An Introduction (Part 2)}{Exercise 3}{21st February 2014}
\runningheadrule
\runningfooter{}{\thepage}{}
\runningfootrule

\title{Exercise 3 - Referencing}
\author{UGC `\LaTeX: An Introduction (Part 2)' Training Course}
\date{February 21st 2014}


\begin{document}
\maketitle

\fbox{\parbox{0.9\textwidth}{In this exercise, we will start to look at including bibliographies and referencing within our \LaTeX\ documents}}

\vspace{0.2in}

\begin{questions}

\question
Add a \texttt{thebibliography} environment to your document.
\question
Add some references to your bibliography, and cite them within your text.
\question
Compile your document and ensure the references and citations appear correctly.
\question
Remove your \texttt{thebibliography} environment and citations. Create an empty ~\texttt{.bib} file in the same directory as your current \LaTeX\ file.
\question
Add some \BibTeX\ entries to your bib file. You can make them up, or use real papers by finding the \BibTeX\ online or exporting it from your current reference manager.
\question
Add some citations to your document using the \texttt{{\textbackslash}cite} command.
\question
Compile your document (following the steps in the lecture slides - remember to use \BibTeX\ as well as \texttt{pdflatex}) and verify your references and citations appear correctly.
\question
Experiment with changing the bibliography style. Observe the differences between styles in terms of how the citations appear within the document and how the references are organised in the bibliography.
\end{questions}

\end{document}